\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-04-25 design.tex
add more design writing

In Landslide's view of the world, timer interrupts are the only source of nondeterminism for the guest kernel, and controlling when they occur theoretically allows for complete control over the concurrent behaviour of the test case. However, it is more useful to view the concurrent behaviour with a higher-level abstraction, in terms of the set of runnable threads and the ability to preempt the currently-running thread with any different runnable one.
% TODO

@@

\subsubsection{Thread Scheduling}
% TODO

@@

\subsubsection{Partial-Order Reduction}
\label{sec:techniques-por}
% talk about the all-ancestors vs induction thing
% talk about ignoring runqueue accesses, etc
% TODO

\subsubsection{Selective Ignorance}
% TODO

@@

\begin{enumerate}
	\item If the kernel has panicked, Landslide prints the message used in the panic/assertion.
	\item If a use-after-free bug is found, Landslide prints information about the most-recently-freed chunk containing the accessed address: the stack trace and TID both for when it was allocated and freed.
	\item If deadlock is detected (currently only using the annotations for yielding mutexes), Landslide prints the cycle of TIDs that are blocked on each other.
	\item If a memory leak is detected, Landslide prints 
\end{enumerate}

>>>>

% TODO

@@

\subsubsection{Thread Scheduling}

In Landslide's view of the world, timer interrupts are the only source of nondeterminism for the guest kernel, and controlling when they occur theoretically allows for complete control over the concurrent behaviour of the test case. However, it is more useful to view the concurrent behaviour with a higher-level abstraction, in terms of the set of runnable threads and the ability to preempt the currently-running thread with any different runnable one.

Landslide's scheduling technique, called the {\em schedule in-flight}, involves successive triggering of timer interrupts to trigger context switches until the desired thread begins to run. % TODO: make an algorithm listing for the schedule-in-flight alg

@@

\subsection{Partial-Order Reduction}
\label{sec:techniques-por}

We make use of Dynamic Partial-Order Reduction, the state-space pruning algorithm presented in \cite{dpor}. Here we discuss the specifics of implementing DPOR in our environment.

\subsubsection{Happens-Before Relation}
% TODO

\subsubsection{Memory Independence Relation}

The independence relation expresses which transitions do not read-and-write or write-and-write to the same shared memory addresses.
% talk about ignoring runqueue accesses, etc TODO

\subsubsection{Coarse Granularity}
% talk about the all-ancestors vs induction thing TODO

@@

\begin{enumerate}
	\item If the kernel has panicked, Landslide prints the message used in the panic/assertion.
	\item If a use-after-free bug is found, Landslide prints information about the most-recently-freed chunk containing the accessed address: the stack trace and TID both for when it was allocated and freed.
	\item If deadlock is detected, Landslide prints the cycle of TIDs that are blocked on each other.\footnote{This currently only works when using the annotations for yielding mutexes, though it is not difficult to implement more generally.}
	\item If a memory leak is suspected, Landslide prints how many bytes bigger the heap is after the test ended than when the test began.\footnote{Future feature: Printing when-allocated stack traces for each suspicious heap chunk.}
	\item If an infinite loop is suspected, depending on which heuristic was triggered, Landslide prints either the number of instructions since the last decision point (and the previous average) or the current branch depth (and the previous average).
\end{enumerate}
